A generalized definition of multidimensional item response theory parameters

### 2022-08-11 output/paper_draft/paper_M2PLM_parameters.Rmd
Minor errata corrected in the manuscript draft

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_VECTOR`$.

@@

Notation aside, these equations differ from
Reckase's [-@reckase_difficulty_1985] Equations 3 through 6
only in the term $`r INNER_PROD_INV_DIAG_SQ_PROD`$.
When $`r LS_BASIS`$ is the standard basis,
this term simplifies to an identity matrix
(which results in Equation \@ref(eq:M2PL-formula-polar) through
\@ref(eq:slope-max) simplyfing to rectangular Cartesian coordinates,
i.e. the equations outlined by Reckase).
To compute the direction of the maximum slope,
Reckase leverages on the property that the squared direction cosines sum up to 1
(see Equation 7 therein).
However, this assertion implicitly assumes orthogonal coordinates,
so it does not apply in general to `r DIR_COS_VEC`.<!-- # TODO: To appendix the following, or maybe give for granted? -->
Instead, we may consider the direction cosine vector in $`r LATENT_SPACE_STD`$:

>>>>

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_MODULE`$.

@@

Notation aside, these equations differ from
Reckase's [-@reckase_difficulty_1985] Equations 3 through 6
only in the term $`r INNER_PROD_INV_DIAG_SQ_PROD`$.
When $`r LS_BASIS`$ is the standard basis,
this term simplifies to an identity matrix
(which results in Equation \@ref(eq:M2PL-formula-polar) through
\@ref(eq:slope-max) simplyfing to rectangular Cartesian coordinates,
i.e. the equations outlined by Reckase).
To compute the direction of the maximum slope,
Reckase leverages on the property that the squared direction cosines sum up to 1
(see Equation 7 therein).
However, this assertion implicitly assumes orthogonal coordinates,
so it does not apply in general to $`r DIR_COS_VEC`$.<!-- # TODO: To appendix the following, or maybe give for granted? -->
Instead, we may consider the direction cosine vector in $`r LATENT_SPACE_STD`$:
